%%%%%%%%%%%%
%%        
%%   Préambule  
%%              

\documentclass[11pt]{report}
\usepackage[latin1]{inputenc}
\usepackage[british]{babel}
\usepackage[pdftex,pdfborder={0 0 0}]{hyperref}


\makeatletter
\renewcommand{\@chapapp}{}
\makeatother

\renewcommand{\thesection}{\arabic{section}}

%%%%%%%%%%%%
%%                      
%%   Document  
%%             
%%%%%%%%%%%%

 \begin{document}
% Informations du fichier pdf
\hypersetup{ % Modifiez la valeur des champs suivants
    pdfauthor   = {R\'{e}my SAKSIK},
    pdftitle    = {Report},
    pdfsubject  = {Report},
    pdfkeywords = {},
    pdfcreator  = {PDFLaTeX},
    pdfproducer = {PDFLaTeX}
    }
  %%%%%%%%%%%%
%  Page de titre 
%%%%%%%%%%%%
    \title{REPORT}
    \author { 
    Etienne PAPEGNIES\\
    Remy SAKSIK\\
    Hamed SARGAZI\\
    Naima EL MISSOURI\\
    Avignon University\\
    France\\
}
   \maketitle
 % \cleardoublepage

 %\setcounter{tocdepth}{1}
\setcounter{secnumdepth}{1}



%%%%%%%%%%%%%%
% Table des matières 	
%%%%%%%%%%%%%%
    \tableofcontents
%%%%%%%%%%%%%%%%%%
    
   \chapter*{Introduction}  
   \addcontentsline{toc}{chapter}{Introduction} % pour ajouter l'introduction à la table des matières
   
~~~~~~~~~We have developped a library for manipulating very large integers, the number of digits exceeds the capacity of
representation of integers supported by the conventional types.
In my capacity of project manager, I was in charge of dividing the labour, which I did by assigning the coding work
to developpers and putting other members in charge of redacting the documentation. 
   
    \chapter*{production}  
    \addcontentsline{toc}{chapter}{production} % pour ajouter l'introduction à la table des matières
   \section{R\'{e}my SAKSIK}

   Project managers and head of the coding team.
        \begin{itemize}
            \item Processing function for substraction and division
            \item Processing function of the substraction and division
            \item Producer of the input/output module to files
            \item Writer of the documents

        \end{itemize}
    \section{Etienne PAPEGNIES}

  Designer of the project object model.
        \begin{itemize}
           \item Creator of reservation module memory space.
            \item Processing function of the multiplication and addition
            \item Producer of arithmetic function of multiplication and subtraction
        \end{itemize}

   \section{Hamed SARGAZI}

 Head of testing and performance.
        \begin{itemize}
            \item Writer of the scope estatment.
            \item Creator of test plan.
	    \item Writer of test plan.
            \item User test scripts.
        \end{itemize}

 \section{Naima EL MISSOURI}
menber of the coding team
        \begin{itemize}
            \item Realization of the functionality of factorial.
	    \item Basic function of the user for the realization of the factorial
        \end{itemize}

 \chapter*{problems encountered and solution made }  
    \addcontentsline{toc}{chapter}{problems encountered and solution made} % pour ajouter l'introduction à la table des matières
~~~~~~~~~We chose not to start programming object (about speed) but we've realized in time that it was not good.
After different tests on the use of memory, of very many memory leaks were observed.

~~~~~~~~~So we opt for the production of clean code and rehabilitation following features of the object model.

 \chapter*{Conclusion}  
    \addcontentsline{toc}{chapter}{Conclusion} 

~~~~~~~~~We have accomplished this project with high and low that few know a team d\'{e}vellopement.
We have demonstrated poor organization at the start but we revised it very quickly which allowed us to finish in time.
This was a project that we qualify rewarding working conditions as a team.



\end{document}




